
\documentclass[11pt]{article}

\usepackage{xcolor}
\usepackage{chngcntr}
\usepackage{enumitem}
\usepackage[small]{titlesec}
\newlist{paragraphlist}{enumerate}{1}


\setlist[paragraphlist,1]{leftmargin=*,label={\bfseries \arabic*}}

\counterwithin{paragraphlisti}{subsubsection}




\title{{\Huge   Task Schedule}}

\author{Stav Alfi and Shachar Rosenman}

\date{\today}

\begin{document}
\maketitle



\begin{Large}
Feature 1: Getting started. \colorbox{gray!10}{IN PROGRESS}
\end{Large}

\begin{enumerate}[label=(\roman*)]

\item Understand what .torrent files are.
\item How to communicate with a tracker.
\item How to communicate with a peer.
\item Paper - Introduction and related work.
\end{enumerate}



\section{PBI-1: Create work space. DONE}
\begin{enumerate}
\item Git repository – GitHub. \colorbox{gray!20}{DONE}
\item Configure branch protection + pull request.  \colorbox{gray!20}{DONE}
\item Create automatic build: compilation + Units tests + cucumber tests – Travis-CI.  \colorbox{gray!20}{DONE}
\end{enumerate}

\section{PBI-2: Shachar training. IN PROGRESS}
\begin{enumerate}
\item Git - add,commit,branch,checkout,merge,push,fetch.  \colorbox{gray!20}{IN PROGRESS} (shachar)
\item Github - pull requests. \colorbox{gray!20}{IN PROGRESS} (shachar)
\item Travis-CI - understand what it is and how to run a build. \colorbox{gray!20}{IN PROGRESS} (shachar)
\item Cucucmber - feature,scenario,steps,step-definition,debug steps. \colorbox{gray!20}{IN PROGRESS} (shachar)
\end{enumerate}

\section{PBI-3: Fully understand torrent file structure. DONE}
\begin{enumerate}
\item List of information types which are saved in a .torrent file. \colorbox{gray!20}{DONE} (shachar, stav)
\item Understand how much parts there are for a file. Where can we get this information for each torrent \item file. \colorbox{gray!20}{DONE} (shachar, stav)
\item What library in java we need to use to read and analyze .torrent files. \colorbox{gray!20}{DONE} (shachar, stav)
\end{enumerate}

\section{PBI-4: Get details about a given tracker. DONE}
\begin{enumerate}
\item Find the protocol and port which enable us to communicate with a given tracker. \colorbox{gray!20}{DONE} (stav)
\item List the methods we can run on a given tracker. \colorbox{gray!20}{DONE} (stav)
\item Get list of peers information from this tracker on a specific torrent. \colorbox{gray!20}{DONE} (stav)
\item Extract a peers IP from a seeder information. \colorbox{gray!20}{DONE} (stav)
\end{enumerate}

\section{PBI-5: Communicate with a seeder. IN PROGRESS}
\begin{enumerate}
\item Find the protocol and port which enable us to communicate with a seeder. \colorbox{gray!20}{IN PROGRESS} (stav)
\item List the methods we can run on a given seeder. \colorbox{gray!20}{NOT STARTED}
\item Ask if he have the file specified by the torrent file. \colorbox{gray!20}{NOT STARTED}
\item Which parts a seeder have from a file until now. \colorbox{gray!20}{NOT STARTED}
\item Download one random part from a seeder. \colorbox{gray!20}{NOT STARTED}
\end{enumerate}

\section{PBI-6: Others. NOT STARTED}
\begin{enumerate}
\item Learn how to work with latex.
\item transform this file to latex.
\item Create a paper on: \colorbox{gray!20}{NOT STARTED} 14.12.17
\begin{enumerate}
\item What are we building.
\item How client torrent application work.
\item What our application do,add,won't do compared to other client torrent applications.
\item How our application will work including technologies.
\end{enumerate}
\end{enumerate}



\end{document}
